\documentclass[12pt]{article}

\usepackage{geometry}
\geometry{margin=1in}

\title{Career Help Platform Design Specification}
\date{}

\begin{document}
\maketitle

\section{Overview}
This document provides a detailed design specification of the Career Help Platform. 
It breaks down every major component of the system, including pages, modules, tools, and required dependencies.

\section{Page Breakdown}
\subsection{Home Page}
Displays introduction and allows user to begin selecting a career path.

\subsection{Career Selection Page}
Contains a dropdown list of careers and a button to generate recommendations.

\subsection{Recommendations Page}
Displays colleges, certificates, internships, jobs, and experience required for the chosen career.

\section{Component Breakdown}
\begin{itemize}
    \item \textbf{Career Selector Module:} Accepts user input.
    \item \textbf{Recommendation Engine:} Retrieves data based on the career.
    \item \textbf{Data Layer:} Stored as JSON or database.
    \item \textbf{Counseling Module (future):} Handles paid 1-on-1 sessions.
\end{itemize}

\section{Dependencies and Libraries}
Planned dependencies:
\begin{itemize}
    \item Python Flask (backend)
    \item HTML/CSS/JavaScript (frontend)
    \item JSON data storage
\end{itemize}

\section{Docker Requirements}
\begin{itemize}
    \item Python 3.10 base image
    \item Copy project files into container
    \item Expose port 5000
\end{itemize}


\section{Snapshot 2 Design: AI Career Roadmap Generator}

\subsection{Chatbot Interaction Design}
The primary entry point for the new feature is the chatbot-style UI. The following interaction pattern is expected:

\begin{itemize}
    \item The user types a natural language request for a career roadmap.
    \item The UI displays the user message in the conversation history.
    \item The frontend sends the message and any structured form data to the backend API.
    \item The UI displays a loading indicator while the roadmap is generated.
    \item The final roadmap is rendered as a series of sections or bullet lists within the chat window.
\end{itemize}

\subsection{Backend Endpoint Specification}
A new backend endpoint is defined conceptually as:

\begin{itemize}
    \item \textbf{Method:} POST
    \item \textbf{Path:} \texttt{/career-roadmap}
    \item \textbf{Request Body:} JSON containing major, interests, experience level, and target career goal.
    \item \textbf{Response:} JSON structure including one or more phases, each with recommended actions.
\end{itemize}

\subsection{Integration with Existing Components}
The Career Roadmap Generator reuses and extends the planned recommendation engine by:

\begin{itemize}
    \item Adding AI-generated narrative guidance on top of static recommendations.
    \item Allowing the same data layer (for example, predefined careers or skills) to be referenced in the AI prompts.
    \item Keeping the design flexible enough to plug in future features like class schedule search or live internship feeds.
\end{itemize}



\section{Snapshot 3 Design: Internship Opportunities and Guidance}

\subsection{UI and Interaction}
The chatbot accepts internship-specific queries and displays results in structured format.

\subsection{Backend Conceptual Endpoints}
\begin{itemize}
\item POST /internships/search
\item POST /internships/guide
\end{itemize}

\subsection{Integration}
Internship module integrates with intent router and may leverage roadmap data.

\end{document}

\section{Snapshot 4 Design: Final Refinements and System Completion}

Snapshot 4 focuses on finalizing the Career Help Platform for delivery. 
Rather than introducing new features, this phase ensures that the UI, backend services, 
and supporting documentation are consistent, stable, and aligned with the project’s intended functionality.

\subsection{UI/UX Refinements}
Several design updates were made to improve clarity, readability, and consistency across the platform:

\begin{itemize}
    \item Standardized spacing, typography, and component sizing across all pages.
    \item Improved layout structure for roadmap and internship results (card-based formatting).
    \item Updated chatbot message bubbles for clearer distinction between user and system messages.
    \item Ensured consistent styling for certificate, internship, and job lists.
    \item Added responsive design adjustments for smaller screens.
\end{itemize}

\subsection{Navigation and Page Structure Updates}
Snapshot 4 finalizes the system’s page-level design with the following improvements:

\begin{itemize}
    \item Streamlined top-level navigation for Roadmaps, Internships, Certificates, and Jobs.
    \item Updated routing configurations to reduce unnecessary page reloads.
    \item Ensured that each feature is reachable within two clicks or fewer.
\end{itemize}

\subsection{Backend Design Stabilization}
No new backend modules were introduced during Snapshot 4; however, several improvements were finalized:

\begin{itemize}
    \item Cleanup of unused parameters and draft endpoints left from early snapshots.
    \item Standardized API response formats across all services (roadmaps, internships, certificates).
    \item Added error-handling patterns to support invalid or incomplete chatbot requests.
    \item Ensured that both roadmap and internship modules return structured JSON compatible with shared UI components.
\end{itemize}

\subsection{Workflow and System Diagram Updates}
Snapshot 4 includes updates to the workflow to reflect the final system state:

\begin{enumerate}
    \item The user interacts through a React-powered UI or chatbot interface.
    \item The frontend sends structured or natural language input to the backend.
    \item The backend routes the request to either the Career Roadmap Service or Internship Guidance Module.
    \item Services retrieve or generate data and return structured JSON responses.
    \item The UI renders results using unified card layouts and sectioned responses.
\end{enumerate}

\subsection{Final Component Summary}
At the completion of Snapshot 4, the full system design includes:

\begin{itemize}
    \item \textbf{Chatbot UI:} Central interaction method supporting roadmap and internship queries.
    \item \textbf{Career Roadmap Generator:} Provides phase-based academic and skill guidance.
    \item \textbf{Internship Opportunities Module:} Supplies internship listings and application strategies.
    \item \textbf{Certificate Exploration:} Lists recommended certifications tied to career paths.
    \item \textbf{Job Overview:} Displays example entry-level jobs aligned with selected fields.
    \item \textbf{Unified Data Layer:} Centralized source of career, internship, and certification information.
\end{itemize}

\subsection{Deployment and Docker Integration}
Snapshot 4 introduces finalized deployment support:

\begin{itemize}
    \item A \texttt{docker-compose.yml} file defining services for frontend, backend, and database.
    \item Consistent environment variable usage for API services.
    \item Stable container networking allowing seamless UI–API–database communication.
\end{itemize}

\subsection{Testing and Stability Considerations}
Design updates include support for complete system testing:

\begin{itemize}
    \item TestRail Snapshot 4 regression testing validates roadmap generation, internship guidance, and UI workflows.
    \item Error messages, loading indicators, and fallback responses were refined to ensure usability.
    \item All major components now produce deterministic and readable output.
\end{itemize}

\section*{Snapshot 4 Summary}
The final design delivers a polished, user-friendly experience with clear workflows, responsive components, 
and a fully documented system architecture suitable for future enhancements or deployment.

