\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}

\title{Software Design Document (SDD) \\ Version 4.0 \\ Career Help Platform}
\date{}

\begin{document}
\maketitle

\section*{Version Table}
\begin{tabular}{|c|p{8cm}|c|}
\hline
Version & Description & Date \\ \hline
1.0 & Initial system design (Snapshot 1) & -- \\ \hline
2.0 & Added AI Career Roadmap Generator (Snapshot 2) & -- \\ \hline
3.0 & Added Internship Opportunities and Guidance module (Snapshot 3) & -- \\ \hline
4.0 & Final design updates, workflow completion, and documentation cleanup (Snapshot 4) & -- \\ \hline
\end{tabular}

\section{Introduction}
\subsection{Purpose}
This document describes the final design of the Career Help Platform, including architecture, components, and data flow. 

\subsection{Scope}
The platform helps students and job seekers explore careers, view certificates, internships, and jobs, and receive structured guidance.

\section{System Architecture}
\subsection{High-Level Overview}
The system follows a client--server model:
\begin{itemize}
    \item \textbf{Frontend:} React-based single-page application.
    \item \textbf{Backend:} Node.js + Express API server.
    \item \textbf{Database:} MongoDB storing user data, career data, and curated resources.
    \item \textbf{Containerization:} Docker and docker-compose used to orchestrate services.
\end{itemize}

\subsection{Final Workflow (Narrative)}
\begin{enumerate}
    \item User accesses the Career Help Platform via browser.
    \item The React frontend sends requests to the Express backend using REST APIs.
    \item The backend queries MongoDB and/or internal logic to generate recommendations.
    \item Responses are returned as JSON and rendered into UI components (cards, lists, sections).
\end{enumerate}

\section{Major Components}
\subsection{Frontend Components}
\begin{itemize}
    \item Navigation bar and layout components.
    \item Career Roadmap Generator views.
    \item Internship Opportunities and Application Guidance views.
    \item Shared card/list components for jobs, internships, and certificates.
\end{itemize}

\subsection{Backend Components}
\begin{itemize}
    \item Route handlers for careers, internships, jobs, and certificates.
    \item Roadmap generation logic (AI or rule-based stub).
    \item Internship recommendation and guidance logic.
\end{itemize}

\section{User Interface Design}
\subsection{Key Screens}
\begin{itemize}
    \item Home page providing an overview.
    \item Career roadmap page where users input interests and goals.
    \item Internship page with filters and guidance text.
    \item Certificates page listing education/training options.
\end{itemize}

\section{Database Design}
At minimum, the system stores:
\begin{itemize}
    \item Collections for career paths.
    \item Collections for internships (mock or static data).
    \item Collections for certificate resources.
\end{itemize}

\section{Glossary}
\begin{itemize}
    \item \textbf{API} – Application Programming Interface.
    \item \textbf{UI} – User Interface.
    \item \textbf{SPA} – Single Page Application.
\end{itemize}

\section{References}
Official documentation for React, Express, MongoDB, and Docker.

\end{document}
