\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}

\title{Software Requirements Specification (SRS) \\ Version 4.0 \\ Career Help Platform}
\date{}

\begin{document}
\maketitle

\section*{Version Table}
\begin{tabular}{|c|p{8cm}|c|}
\hline
Version & Description & Date \\ \hline
1.0 & Initial requirements defined for core platform & -- \\ \hline
2.0 & Requirements for AI Career Roadmap Generator added & -- \\ \hline
3.0 & Requirements for Internship Opportunities and Guidance added & -- \\ \hline
4.0 & Final requirement updates and clean up (Snapshot 4) & -- \\ \hline
\end{tabular}

\section{Introduction}
\subsection{Purpose}
This SRS describes the final functional and non-functional requirements for the Career Help Platform.

\subsection{Intended Audience}
Developers, testers, instructors, and stakeholders involved in evaluating or maintaining the project.

\subsection{Overview}
The system supports:
\begin{itemize}
    \item Career roadmap generation.
    \item Internship discovery and guidance.
    \item Certificate and job exploration.
\end{itemize}

\section{External Interface Requirements}
\subsection{User Interface}
\begin{itemize}
    \item The user interacts with a responsive web UI.
    \item Key pages: home, career roadmap, internships, certificates, jobs.
    \item Information is shown using cards, lists, and simple forms.
\end{itemize}

\subsection{Software Interfaces}
\begin{itemize}
    \item React frontend communicates with Express backend via REST APIs.
    \item Backend connects to MongoDB database.
    \item Optionally, external APIs may be used for jobs/internships in future versions.
\end{itemize}

\section{Functional Requirements}
\subsection{Career Roadmap}
\begin{itemize}
    \item FR-CR1: System must accept inputs such as major, interests, and target role.
    \item FR-CR2: System must return a multi-step roadmap with milestones.
\end{itemize}

\subsection{Internship Opportunities}
\begin{itemize}
    \item FR-INT1: System must allow users to browse internship options.
    \item FR-INT2: System must display basic information (title, location, area).
    \item FR-INT3: System must provide guidance text for applications.
\end{itemize}

\section{Legal and Ethical Considerations}
\begin{itemize}
    \item The platform should avoid storing highly sensitive personal data.
    \item Recommendations should not be biased toward specific institutions or employers without justification.
    \item Any external data sources must comply with their respective terms of use.
\end{itemize}

\section{Future Requirements}
Possible future requirements include:
\begin{itemize}
    \item Authentication and personalized profiles.
    \item Role-based dashboards.
    \item Deeper integration with external job APIs.
\end{itemize}

\end{document}
